Parties, Models, Mobsters\newline {\fontsize{11}{15}\selectfont A New Implementation of Model-Based Recursive Partitioning in R}

### 2014-03-18 pkg/partykit/inst/NUS-2014/modelparty.Rnw
small touch-ups
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@492 255f4249-2263-4417-b1ea-8498779e27a7
small touch-ups
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@505 255f4249-2263-4417-b1ea-8498779e27a7

\textbf{Main addition:} Data handling for regressor and partitioning variables.
\begin{itemize}
  \item The \emph{Formula} package is used for Two-part formulas, e.g.,\\
    \code{y ~ x1 + x2 | z1 + z2 + z3}.
  \item The corresponding terms are stored for the combined
    model and only for the partitioning variables.
\end{itemize}

@@

Hothorn T, Zeileis A (2014).
 \textit{partykit: A Toolkit for Recursive Partytioning.}
 R~package version~0.2-0.
 URL~\url{http://R-Forge.R-project.org/projects/partykit/}

>>>>

\textbf{Main addition:} Data handling for regressor and partitioning variables.
\begin{itemize}
  \item The \emph{Formula} package is used for two-part formulas, e.g.,\\
    \code{y ~ x1 + x2 | z1 + z2 + z3}.
  \item The corresponding terms are stored for the combined
    model and only for the partitioning variables.
\end{itemize}

@@

Hothorn T, Zeileis A (2014).
 \textit{partykit: A Toolkit for Recursive Partytioning.}
 R~package version~0.8-0.
 URL~\url{http://R-Forge.R-project.org/projects/partykit/}
